Self Regulation Ontology Retest Data Report

### 2017-04-23 SRO_Report.Rmd
added table with filtering
improved bootstrapping function to output specific metrics

**ADD FILTER TO DATA TABLE FOR THIS DISPLAY INSTEAD OF MAKING TWO SEPARATE TABLES**

- Demographics are excluded from this list of variables (because they are saved for predictive analyses).  
- Holt and Laury test-retest is the worst for *surveys*. But note that this is not a survey that has been studied extensively psychometrically like others. This is more similar to our tasks (one that is used more often by economists). In previous data I have worked with retest reliablities for this task was ~.35 so the results here are in line with this.  
- Otherwise the lowest survey reliabilities are 0.5.

```{r}

@@

bootstrap_relialibility = function(metric = c('icc', 'spearman', 'eta_sq', 'sem'), dv_var){
  tmp_sample = sample_workers()
  out_df = data.frame(dv = dv_var)
  out_df$icc = get_icc(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  out_df$spearman = get_spearman(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  out_df$eta_sq = get_eta(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  out_df$sem = get_sem(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  return(out_df)
}

>>>>

- Note that this table can be sorted by different metrics, filtered for specific values for each column and is searchable.  
- Demographics are excluded from this list of variables (because they are saved for predictive analyses).  
- Holt and Laury test-retest is the worst for *surveys*. But note that this is not a survey that has been studied extensively psychometrically like others. This is more similar to our tasks (one that is used more often by economists). In previous data I have worked with retest reliablities for this task was ~.35 so the results here are in line with this.  
- Otherwise the lowest survey reliabilities are 0.5.

```{r}
datatable(rel_df, filter = 'top')
```

@@

bootstrap_relialibility = function(metric = c('icc', 'spearman', 'eta_sq', 'sem'), dv_var){
  tmp_sample = sample_workers()
  out_df = data.frame(dv = dv_var)
  if('icc' %in% metric){
    out_df$icc = get_icc(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  if('spearman' %in% metric){
    out_df$spearman = get_spearman(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  if('eta_sq' %in% metric){
    out_df$eta_sq = get_eta(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  if('sem' %in% metric){
    out_df$sem = get_sem(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  return(out_df)
}
